SoK: Defenses Against Web Application Attacks: From Research Approaches to Practical Tools

### 2014-11-13 docs/questioning.tex
minor changes

\title{SoK: The Evolution of Defenses Against Web Application Attacks}

@@

  In this paper, we systematize the existing knowledge on
  various defense mechanisms against source code injection attacks by proposing
  a model that highlights the key weaknesses that enable these attacks,
  and provides a common perspective for the different defenses.
  We then categorize and analyze the various defense mechanisms that
  have been developed, based on their accuracy, performance,
  deployment, security, and availability properties.
  Accuracy is of particular importance, as our findings show that many defense
  mechanisms have been tested in a poor manner. In addition, we observe
  that some mechanisms can be bypassed by attackers with knowledge
  of how the mechanisms work.
  By comparing the existing defenses and identifying their common
  characteristics, we help researchers and practitioners to choose or
  modify defenses according to their needs, as well as designers of
  new approaches in developing more effective mechanisms.

@@

\begin{enumerate}
\item We provide an exploitation model that puts application attacks
  based on source code injection under a common
  perspective.
\item We categorize and analyze proposed defenses using a set of
  criteria that are important for building protection mechanisms.
\item We find that researchers often test the accuracy
  of their mechanisms poorly. 
\item We also find that researchers do not often make their mechanisms
  available to the community, thus no one can either use them,
  or replicate their experiments.
\item We discuss how our observations may be the main reasons why the
  mechanisms are not adopted in practice.
\item We discuss what are the necessary criteria for new mechanisms
  and how our work can help researchers to design new countermeasures.
\end{enumerate}

@@

We hope that the exploitation model, analysis, and observations that
emerged from our research can be a reference point for researchers who
wish to develop new countermeasures against web application
attacks.

>>>>

\title{SoK: Defenses Against Web Application Attacks: From Research
  Approaches to Practical Tools}

@@

  In this paper, we systematize the existing knowledge on
  various defense mechanisms against source code injection attacks by proposing
  a model that highlights the key weaknesses that enable these attacks,
  and provides a common perspective for the different defenses.
  We then categorize and analyze the various defense mechanisms that
  have been developed, based on their accuracy, performance,
  deployment, security, and availability properties.
  We discuss the results of our analysis, with emphasis on factors
  that may hinder the widespread adoption of attack detection
  mechanisms in practice.

@@

\begin{enumerate}
\item We provide an exploitation model that puts application attacks
  based on source code injection under a common
  perspective.
\item We categorize and analyze proposed defenses using a set of
  criteria that are important for building protection mechanisms.
\item We discuss the issues that arise from our analysis. We put
  emphasis on factors that may hinder widespread adoption of
  approaches and the translation of tools from research to practice.
\end{enumerate}

@@

We hope that the exploitation model, analysis, and observations that
emerged from our research can be a reference point for researchers who
wish to develop new, practical countermeasures against web application
attacks.
